Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-12 output/latex/manuscript.tex
latex: update supplementary material tex file

\clearpage
\hypertarget{supplementary-material}{%
\subsection{Supplementary material}\label{supplementary-material}}

\hypertarget{regression-model-for-lv-trait-associations}{%
\subsubsection{Regression model for LV-trait associations}\label{regression-model-for-lv-trait-associations}}

\hypertarget{sm:reg:null_sim}{%
\paragraph{Supplementary Note 1: mean type I error rates and calibration of LV-based regression model}\label{sm:reg:null_sim}}

@@

We also detected other LVs with higher-than-expected mean type I errors for both the GLS and OLS models, although they don't have a relatively large number of adjacent genes at the top.
One example is LV914, shown in Figure \ref{fig:reg:nulls:qqplot:lv914}.
Inflation in these LVs might be explained by inaccuracies in correlation estimates between the individual-level MultiXcan model and its summary-based version (see Methods).
Therefore, we flagged those with a type I error rate larger than 0.07 (127 LVs) and excluded them from our main analyses.

@@

\clearpage
\hypertarget{crispr-cas9}{%
\subsubsection{CRISPR-Cas9}\label{crispr-cas9}}

\hypertarget{screening-steps}{%
\paragraph{Screening steps}\label{screening-steps}}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:table1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/table1.png}
\caption{}\label{fig:sup:crispr:table1}
}
\end{figure}

@@

\hypertarget{gene-modules-enrichment-for-lipids-gene-sets}{%
\paragraph{Gene modules enrichment for lipids gene-sets}\label{gene-modules-enrichment-for-lipids-gene-sets}}

@@

\clearpage
\hypertarget{consensus-clustering-of-traits}{%
\subsubsection{Consensus clustering of traits}\label{consensus-clustering-of-traits}}

\hypertarget{sm:clustering:null_sim}{%
\paragraph{Supplementary Note 2: Cluster analyses under the null hypothesis of no structure in the data}\label{sm:clustering:null_sim}}

@@

\hypertarget{cluster-specific-and-general-transcriptional-processes-associated-with-disease}{%
\paragraph{Cluster-specific and general transcriptional processes associated with disease}\label{cluster-specific-and-general-transcriptional-processes-associated-with-disease}}

@@

>>>>

\clearpage

\hypertarget{supplementary-material}{%
\subsection{Supplementary material}\label{supplementary-material}}

\hypertarget{sm:reg:null_sim}{%
\subsubsection{Supplementary Note 1: mean type I error rates and calibration of LV-based regression model}\label{sm:reg:null_sim}}

@@

We also detected other LVs with higher-than-expected mean type I errors for both the GLS and OLS models, although they don't have a relatively large number of adjacent genes at the top.
One example is LV914, shown in Figure \ref{fig:reg:nulls:qqplot:lv914}.
Inflation in these LVs might be explained by inaccuracies in correlation estimates between the individual-level MultiXcan model and its summary-based version (see Methods).
Therefore, we flagged those with a type I error rate larger than 0.07 (127 LVs) and excluded them from our main analyses.
We didn't see signs of inflation when applying the method in real data (Figure \ref{fig:reg:real:qqplots}).

@@

\clearpage

\hypertarget{crispr-cas9}{%
\subsubsection{CRISPR-Cas9}\label{crispr-cas9}}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:table1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/table1.png}
\caption{\textbf{Primers for generating illumina libraries.}}\label{fig:sup:crispr:table1}
}
\end{figure}

@@

\clearpage

\hypertarget{gene-modules-enrichment-for-lipids-gene-sets}{%
\subsubsection{Gene modules enrichment for lipids gene-sets}\label{gene-modules-enrichment-for-lipids-gene-sets}}

@@

\clearpage

\hypertarget{sm:clustering:null_sim}{%
\subsubsection{Supplementary Note 2: Cluster analyses under the null hypothesis of no structure in the data}\label{sm:clustering:null_sim}}

@@

\clearpage

\hypertarget{cluster-specific-and-general-transcriptional-processes-associated-with-disease}{%
\subsubsection{Cluster-specific and general transcriptional processes associated with disease}\label{cluster-specific-and-general-transcriptional-processes-associated-with-disease}}

@@

\clearpage
